---
title: "Risk Adjusted Outcomes for Urologic Oncology"
subtitle: "OSHPD Data Descriptions"
author: "Anobel Y Odisho, Ruth Etzioni, John L Gore"
date: "`r Sys.Date()`"
output: 
  tufterhandout::html_tufte_handout:
        theme: cosmo
        css: floating.css
        toc: yes
params:
    cohort: "Cystectomy"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width=12, cache=F)
```

<!--- this inline CSS style is to alter horizontal table padding for stargazer tables -->
<style>
  td {
    padding-left: 3px;
    padding-right: 3px;
  }
</style>
  
```{r packages, cache=F}
# Data Cleaning Packages
library(lubridate)
library(plyr)
library(dplyr)
library(stringr)
library(tidyr)

# Graphics Packages
library(DT)
library(ggplot2)
library(ggthemes)
library(knitr)
library(RColorBrewer)
library(stargazer)

# Specialty/Stats Packages
library(icd9)
library(ROCR)
library(lme4)
```

```{r constants.functions}
bg <- "#FCFCFA"
main1 <- "#ca0020"
acc1 <- "#f4a582"
main2 <- "#92c5de"
acc2 <- "#0571b0"

# this function takes arguments x=value, y=number of sig figs, prints mean +/- SD in html
prettyMeanSD <- function (x,y) {
  mean <- prettyNum(round(mean(x, na.rm=TRUE),y), big.mark = ",")
  sd <-  prettyNum(round(sd(x, na.rm=TRUE),y), big.mark = ",")
  paste(mean, " &plusmn; ",sd,sep="")
}

prettyMedianIQR <- function (x,y) {
  median <- prettyNum(round(median(x, na.rm=TRUE),y), big.mark = ",")
  tiles <- round(quantile(x, c(.25, .75), na.rm=TRUE),y)
  paste(median, " (",tiles[1], " - ", tiles[2], ")",sep="")
}

rocResult <- function (x) {
  # predict test data result
  pr <- predict(x, newdata=test, allow.new.levels=T)
  pr <- prediction(pr, test$isreadmit30dc)
  auc <- performance(pr, measure="auc") 
  auc <- round(auc@y.values[[1]],4)
  
  # Generate ROC Curve
  roc <- performance(pr, measure="tpr", x.measure="fpr")
  plot(roc, colorize=T)
  cat("AUC:", auc)
}

aucResult <- function(x) {
  # predict test data result
  pr <- predict(x, newdata=test, allow.new.levels=T)
  pr <- prediction(pr, test$isreadmit30dc)
  auc <- performance(pr, measure="auc") 
  auc <- round(auc@y.values[[1]],4)
  return(auc)
}

# create empty list that I will populate with results as we go
auc <- list()
```

```{r loaddata, cache=F}
# Load full dataset (12.5m obs)
# when loading the full data set, in chunk options set cache.lazy=F
# pt <- readRDS(file="rao_workingdata/pt.rds")

# Load lite dataset (sample of 100,000 obs)
ptgu <- readRDS("rao_workingdata/ptgu.rds")

# List variables that will be scaled for models
toscale <- c("agyradmcentered", 
             "elixsum", 
             "bedsMean", "adcMean", "dsh_pctMean", "mcr_pctMean", "cmiMean",
             "ethwhite", "ethblack", "ethlatin", "ethasian", "ethother",
             "medianincome", "capincome", "housevalue",
             "edunohs",	"eduhs", "educollege", "empexec",
             "gini", "iceinc", "iceedu", "iceeth", "hoodzscore", 
             "km", "hours", 
             "los")        
  
# scale and center variables
ptgu[,toscale] <- data.frame(lapply(ptgu[,toscale], scale, center=T, scale=T))
rm(toscale)

# make a disease specific cohort based on the parameter selected
# params <- list(); params$cohort="Cystectomy"
ptgucohort <- ptgu %>% filter(cohort==params$cohort)

# split data into training and validation cohorts
# Set random seed to reproduce results
set.seed(7)

# create an index variable which will allow splitting of training/test data without overlap
ptgucohort$index <- seq(1:nrow(ptgucohort))

# Group by OSHPD_ID, then take a 75% sample for training set
train <- ptgucohort %>%
  group_by(oshpd_id) %>%
  sample_frac(size=0.75, replace=F)
# anything that didnt make it into training set is put into a test set
test <- ptgucohort[!(ptgucohort$index %in% train$index),]

# remove index variables
ptgucohort <- ptgucohort %>% select(-index)
train <- train %>% select(-index)
test <- test %>% select(-index)
```

# Overall Summary
- Total Records: `r nrow(pt)`
- Records in GU specific cohort `r nrow(ptgu)`
- `r kable(t(table(ptgu$cohort)))`

```{r datafields, cache=F, results='asis'}
names(ptgucohort)
```

## Admission Dates
Overall GU Cohort
```{r overallGuCohortAdmissionDates}
kable(t(table(ptgu$cohort)))

ptgu %>%
  ggplot(aes(x=admtdate, weight=1)) + 
  # geom_histogram(aes(y=..density..), fill=main2, alpha=0.3, color="white") +
  geom_density(aes(y=..count.., color=cohort)) +
  scale_color_brewer(palette = "Dark2") + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), 
        legend.background= element_rect(fill=bg), 
        legend.title=element_blank()) + 
  labs(title="Admission Dates for GU Cohort", 
       y="Number of Admissions", 
       x="Admission Date")
```

## Readmissions
Overall 30 day Readmission Rate (%)
```{r overall30dReadmissionRate, results="asis"}
t <- round(100*prop.table(table(ptgu$isreadmit30dc, ptgu$cohort),2),2)
kable(t)
```

## Disposition
Overall Disposition Distribution (%)
```{r overallDispo, results="asis"}
t <- round(100*prop.table(table(ptgu$disp, ptgu$cohort),2),2)
kable(t)
```

## Race/Ethnicity
(%)
```{r overallRace, results="asis"}
t <- round(100*prop.table(table(ptgu$race_grp, ptgu$cohort),2),2)
kable(t)
```

## Payers
Payer Category (%)
```{r overallPayers, results="asis"}
t <- round(100*prop.table(table(ptgu$pay_cat, ptgu$cohort),2),2)
kable(t)
```
<br>

Payer Type (%)
```{r, results="asis"}
t <- round(100*prop.table(table(ptgu$pay_type, ptgu$cohort),2),2)
kable(t)

```

# `r params$cohort` Summary
- Records in `r params$cohort` specific cohort: `r nrow(ptgucohort)`
- For modeling, data split 75/25 into training (n=`r nrow(train)`) and testing (n=`r nrow(test)`) cohorts

# Fixed Effects
## Baseline Model
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex

```{r logmodel1}
m1 <- glm(isreadmit30dc ~ agyradmcentered + sex, data=train, family="binomial")

summary(m1)
rocResult(m1)
auc$m1$formula <- as.character(m1$formula)[3]
auc$m1$auc <- aucResult(m1)
```

Predicted Probability of Readmission
```{r logmodel1preds}
# Generate dataframe of dummy values to calculate predicted probabilities
newm1 <- data.frame(
  agyradmcentered = rep(seq(from=1.8, to=10, length.out = 100),2), 
  sex=factor(c(rep("Male",100), rep("Female",100))))

p1 <- cbind(newm1,predict(m1, newdata = newm1, type="link", se=T))
p1 <- within(p1, {
    PredictedProb <- plogis(fit)
    LL <- plogis(fit - (1.96 * se.fit))
    UL <- plogis(fit + (1.96 * se.fit))
})

ggplot(p1, aes(x = agyradmcentered*10, y = PredictedProb)) + 
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = sex), alpha = 0.1) + 
  geom_line(aes(colour = sex), size = 1) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), 
        legend.background= element_rect(fill=bg), 
        legend.title=element_blank())
```

## Elix Sum
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum

```{r logmodel2}
m2 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum, data=train, family="binomial")

summary(m2)
rocResult(m2)

auc$m2$formula <- as.character(m2$formula)[3]
auc$m2$auc <- aucResult(m2)
```

## Elix Index
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index (30 Categorical Vars)

```{r logmodel3}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex +", paste(elixComorbidNamesAbbrev, collapse="+")))

m3 <- glm(fmla, data=train, family="binomial")

summary(m3)
rocResult(m3)

auc$m3$formula <- as.character(m3$formula)[3]
auc$m3$auc <- aucResult(m3)
```

## Elix, Hospital ID
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index (30 Categorical Vars), Hospital ID as fixed effect
- Turns out this doesnt work due to a large number of hospitals (170), leading to 170 dummy variables.

# Mixed Effects Models
## Baseline ME
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex
- Random Effect: Hospital

```{r MEmodel1}
me1 <- glmer(isreadmit30dc ~ agyradmcentered + sex + (1|oshpd_id), data=train, family="binomial")

# print raw results of regression
summary(me1)
rocResult(me1)

auc$me1$formula <- as.character(me1@call)[2]
auc$me1$auc <- aucResult(me1)

```

## Elix Sum
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum. Hospital as random effect.
- Random Effect: Hospital

```{r MEmodel2}
me2 <- glmer(isreadmit30dc ~ agyradmcentered + sex + elixsum + (1 | oshpd_id), data=train, family="binomial")

# print raw results of regression
summary(me2)
rocResult(me2)
auc$me2$formula <- as.character(me2@call)[2]
auc$me2$auc <- aucResult(me2)
```

## Elix Index
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index Categories. Hospital as random effect.
- Random Effect: Hospital

```{r MEmodel3}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex + ", paste(elixComorbidNamesAbbrev, collapse="+"), " + (1 | oshpd_id)"))

me3 <- glmer(fmla, data=train, family="binomial")

# print raw results of regression
summary(me3)
rocResult(me3)
auc$me3$formula <- as.character(me3@call)[2]
auc$me3$auc <- aucResult(me3)
```

# Models with SES
## Elix Sum, HoodZ
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Neighborhood Z-Score (continuous)

```{r MEmodel4}
me4 <- glm(isreadmit30dc ~ agyradmcentered + sex  + elixsum + hoodzscore, data=train, family="binomial")

# print raw results of regression
summary(me4)
rocResult(me4)
auc$me4$formula <- as.character(me4$call)[2]
auc$me4$auc <- aucResult(me4)
```

## Elix Sum, HoodZ EthW
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Neighborhood Z-Score (continuous), Ethnicity (% white)


```{r MEmodel4a}
me4a <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite, data=train, family="binomial")

# print raw results of regression
summary(me4a)
rocResult(me4a)
auc$me4a$formula <- as.character(me4a$call)[2]
auc$me4a$auc <- aucResult(me4a)
```

## Elix Sum, HoodZ EthB
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Neighborhood Z-Score (continuous), Ethnicity (% black)


```{r MEmodel4b}
me4b <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethblack, data=train, family="binomial")

# print raw results of regression
summary(me4b)
rocResult(me4b)
auc$me4b$formula <- as.character(me4b$call)[2]
auc$me4b$auc <- aucResult(me4b)
```

## Elix Sum, HoodZ Quintile
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Neighborhood Z-Score (quintile)


```{r MEmodel5}
me5 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodquint, data=train, family="binomial")

# print raw results of regression
summary(me5)
rocResult(me5)
auc$me5$formula <- as.character(me5$call)[2]
auc$me5$auc <- aucResult(me5)
```

## Elix Index, HoodZ
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index Categories
- SES: Neighborhood Z-Score 
- Hospital as random effect

```{r MEmodel6}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex + hoodzscore +", paste(elixComorbidNamesAbbrev, collapse="+"), ""))

me6 <- glm(fmla, data=train, family="binomial")

# print raw results of regression
summary(me6)
rocResult(me6)
auc$me6$formula <- fmla[3]
auc$me6$auc <- aucResult(me6)
```

## Elix Index, HoodZ, EthW
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index Categories
- SES: Neighborhood Z-Score, Ethnicity (% white)
- Hospital as random effect

```{r MEmodel6a}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex + hoodzscore + ethwhite + ", paste(elixComorbidNamesAbbrev, collapse="+"), ""))

me6a <- glm(fmla, data=train, family="binomial")

# print raw results of regression
summary(me6a)
rocResult(me6a)
auc$me6a$formula <- fmla[3]
auc$me6a$auc <- aucResult(me6a)
```

## Elix Index, HoodZ, EthB
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index Categories
- SES: Neighborhood Z-Score, Ethnicity (% black)
- Hospital as random effect

```{r MEmodel6b}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex + hoodzscore + ethblack + ", paste(elixComorbidNamesAbbrev, collapse="+"), ""))

me6b <- glm(fmla, data=train, family="binomial")

# print raw results of regression
summary(me6b)
rocResult(me6b)
auc$me6b$formula <- fmla[3]
auc$me6b$auc <- aucResult(me6b)
```

## Elix Index, HoodZ Quintile
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Index Categories
- SES: Neighborhood Z-Score Quintile
- Hospital as random effect

```{r MEmodel7}
fmla <- as.formula(paste("isreadmit30dc ~ agyradmcentered + sex + hoodquint +", paste(elixComorbidNamesAbbrev, collapse="+"), ""))

me7 <- glm(fmla, data=train, family="binomial")

# print raw results of regression
summary(me7)
rocResult(me7)
auc$me7$formula <- as.character(fmla[3])
auc$me7$auc <- aucResult(me7)
```

# SES Categories

## Elix Sum, Eth (White)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Race_group (for the patient, from OSHPD)

```{r MEmodel8}
me8 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + race_grp, data=train, family="binomial")

# print raw results of regression
summary(me8)
rocResult(me8)
auc$me8$formula <- as.character(me8$call)[2]
auc$me8$auc <- aucResult(me8)
```

## Elix Sum, Eth (White)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Ethnicity (% White)

```{r MEmodel9a}
me9a <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + ethwhite, data=train, family="binomial")

# print raw results of regression
summary(me9a)
rocResult(me9a)
auc$me9a$formula <- as.character(me9a$call)[2]
auc$me9a$auc <- aucResult(me9a)
```

## Elix Sum, Eth(AfAm)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Ethnicity (% African American)

```{r MEmodel9}
me9b <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + ethblack, data=train, family="binomial")

# print raw results of regression
summary(me9b)
rocResult(me9b)
auc$me9b$formula <- as.character(me9b$call)[2]
auc$me9b$auc <- aucResult(me9b)
```

## Elix Sum, Income
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Median Income

```{r MEmodel10}
me10 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + medianincome1k, data=train, family="binomial")

# print raw results of regression
summary(me10)
rocResult(me10)
auc$me10$formula <- as.character(me10$call)[2]
auc$me10$auc <- aucResult(me10)
```

## Elix Sum, Home Value
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Median Home Value

```{r MEmodel11}
me11 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + housevalue100k, data=train, family="binomial")

# print raw results of regression
summary(me11)
rocResult(me11)
auc$me11$formula <- as.character(me11$call)[2]
auc$me11$auc <- aucResult(me11)
```

## Elix Sum, Cap Income
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: % households with Capital Income

```{r MEmodel12}
me12 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + capincome, data=train, family="binomial")

# print raw results of regression
summary(me12)
rocResult(me12)
auc$me12$formula <- as.character(me12$call)[2]
auc$me12$auc <- aucResult(me12)
```

## Elix Sum, Edu(NoHS)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Education (% that did not complete HS)

```{r MEmodel13}
me13 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + edunohs, data=train, family="binomial")

# print raw results of regression
summary(me13)
rocResult(me13)
auc$me13$formula <- as.character(me13$call)[2]
auc$me13$auc <- aucResult(me13)
```

## Elix Sum, Edu(No College)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Education (% that did not complete College)

```{r MEmodel14}
me14 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + eduhs, data=train, family="binomial")

# print raw results of regression
summary(me14)
rocResult(me14)
auc$me14$formula <- as.character(me14$call)[2]
auc$me14$auc <- aucResult(me14)
```

## Elix Sum, Edu(College)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Education (% that did complete College)

```{r MEmodel15}
me15 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + educollege, data=train, family="binomial")

# print raw results of regression
summary(me15)
rocResult(me15)
auc$me15$formula <- as.character(me15$call)[2]
auc$me15$auc <- aucResult(me15)
```

## Elix Sum, Employment
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: % Employed in Executive Positions

```{r MEmodel16}
me16 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + empexec, data=train, family="binomial")

# print raw results of regression
summary(me16)
rocResult(me16)
auc$me16$formula <- as.character(me16$call)[2]
auc$me16$auc <- aucResult(me16)
```

## Elix Sum, Diez-Roux independently
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: All components of DiezRoux Index individually

```{r MEmodel17}
me17 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + ethwhite + medianincome1k + housevalue100k + capincome + eduhs + educollege + empexec, data=train, family="binomial")

# print raw results of regression
summary(me17)
rocResult(me17)
auc$me17$formula <- as.character(me17$call)[2]
auc$me17$auc <- aucResult(me17)
```

## Elix Sum, GINI
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: GINI Coefficient of Inequality

```{r MEmodel18}
me18 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + gini, data=train, family="binomial")

# print raw results of regression
summary(me18)
rocResult(me18)
auc$me18$formula <- as.character(me18$call)[2]
auc$me18$auc <- aucResult(me18)
```

## Elix Sum, ICE Income
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Index for Concentration at the Extremes for Income

```{r MEmodel19}
me19 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + iceinc, data=train, family="binomial")

# print raw results of regression
summary(me19)
rocResult(me19)
auc$me19$formula <- as.character(me19$call)[2]
auc$me19$auc <- aucResult(me19)
```

## Elix Sum, ICE Education
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Index for Concentration at the Extremes for Education

```{r MEmodel20}
me20 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + iceedu, data=train, family="binomial")

# print raw results of regression
summary(me20)
rocResult(me20)
auc$me20$formula <- as.character(me20$call)[2]
auc$me20$auc <- aucResult(me20)
```

## Elix Sum, ICE Ethnicity
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Index for Concentration at the Extremes for Ethnicity

```{r MEmodel21}
me21 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + iceeth, data=train, family="binomial")

# print raw results of regression
summary(me21)
rocResult(me21)
auc$me21$formula <- as.character(me21$call)[2]
auc$me21$auc <- aucResult(me21)
```

## Elix Sum, ICE (all)
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Index for Concentration at the Extremes for Income, Ethnicity, Education

```{r MEmodel22}
me22 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + iceinc + iceedu + iceeth, data=train, family="binomial")

# print raw results of regression
summary(me22)
rocResult(me22)
auc$me22$formula <- as.character(me22$call)[2]
auc$me22$auc <- aucResult(me22)
```

# ME with Hosp Factors
## Elix Sum, Volume
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Hospital `r params$cohort` volume
- SES: None

```{r MEmodel23}
me23 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + volume, data=train, family="binomial")

# print raw results of regression
summary(me23)
rocResult(me23)
auc$me23$formula <- as.character(me23$call)[2]
auc$me23$auc <- aucResult(me23)
```

## Elix Sum, Volume Quintile
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Hospital `r params$cohort` volume quintile
- SES: None

```{r MEmodel24}
me24 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + volumequint, data=train, family="binomial")

# print raw results of regression
summary(me24)
rocResult(me24)
auc$me24$formula <- as.character(me24$call)[2]
auc$me24$auc <- aucResult(me24)
```

## Elix Sum, Hospital Beds
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Number of hospital beds
- SES: None

```{r MEmodel25}
me25 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + bedsMean, data=train, family="binomial")

# print raw results of regression
summary(me25)
rocResult(me25)
auc$me25$formula <- as.character(me25$call)[2]
auc$me25$auc <- aucResult(me25)
```

## Elix Sum, Average Daily Census
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Average Daily Census
- SES: None

```{r MEmodel26}
me26 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + adcMean, data=train, family="binomial")

# print raw results of regression
summary(me26)
rocResult(me26)
auc$me26$formula <- as.character(me26$call)[2]
auc$me26$auc <- aucResult(me26)
```

## Elix Sum, Medicare DSH
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Disproportionate Share Index
- SES: None

```{r MEmodel27}
me27 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + dsh_pctMean, data=train, family="binomial")

# print raw results of regression
summary(me27)
rocResult(me27)
auc$me27$formula <- as.character(me27$call)[2]
auc$me27$auc <- aucResult(me27)
```

## Elix Sum, Medicare %
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Meidcare %
- SES: None

```{r MEmodel28}
me28 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + mcr_pctMean, data=train, family="binomial")

# print raw results of regression
summary(me28)
rocResult(me28)
auc$me28$formula <- as.character(me28$call)[2]
auc$me28$auc <- aucResult(me28)
```

## Elix Sum, Case Mix
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Case Mix Index
- SES: None

```{r MEmodel29}
me29 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + cmiMean, data=train, family="binomial")

# print raw results of regression
summary(me29)
rocResult(me29)

auc$me29$formula <- as.character(me29$call)[2]
auc$me29$auc <- aucResult(me29)
```

## Elix Sum, Hosp Comb
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- Hospital: Beds, DSH, Medicare Percentage, Case Mix Index
- SES: None


```{r MEmodel30}
me30 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + bedsMean + dsh_pctMean + mcr_pctMean + cmiMean, data=train, family="binomial")

# print raw results of regression
summary(me30)
rocResult(me30)
auc$me30$formula <- as.character(me30$call)[2]
auc$me30$auc <- aucResult(me30)
```

# Rural, Distance
## Elix Sum, Rural
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Rural

```{r MEmodel31a}
me31a <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + ru, data=train, family="binomial")

# print raw results of regression
summary(me31a)
rocResult(me31a)
auc$me31a$formula <- as.character(me31a$call)[2]
auc$me31a$auc <- aucResult(me31a)
```

## Elix Sum, HoodZscore, Rural
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Diez-Roux, Ethinicity (% white), Rural

```{r MEmodel31b}
me31b <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + ru, data=train, family="binomial")

# print raw results of regression
summary(me31b)
rocResult(me31b)
auc$me31b$formula <- as.character(me31b$call)[2]
auc$me31b$auc <- aucResult(me31b)
```

## Elix Sum, Distance
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Distance

```{r MEmodel31c}
me31c <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + km, data=train, family="binomial")

# print raw results of regression
summary(me31c)
rocResult(me31c)
auc$me31c$formula <- as.character(me31c$call)[2]
auc$me31c$auc <- aucResult(me31c)
```

## Elix Sum, Distance, HoodZ
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Distance, Hood Z Score, Ethnicity (% White)

```{r MEmodel31d}
me31d <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + km, data=train, family="binomial")

# print raw results of regression
summary(me31d)
rocResult(me31d)
auc$me31d$formula <- as.character(me31d$call)[2]
auc$me31d$auc <- aucResult(me31d)
```

## Elix Sum, Distance, Rural
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Distance, Rural

```{r MEmodel31e}
me31e <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + km + ru, data=train, family="binomial")

# print raw results of regression
summary(me31e)
rocResult(me31e)
auc$me31e$formula <- as.character(me31e$call)[2]
auc$me31e$auc <- aucResult(me31e)
```

## Elix Sum, Distance, Rural, HoodZ
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum
- SES: Distance, Rural, Hood Zscore, Ethnicity (% White)

```{r MEmodel31f}
me31f <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + km + ru, data=train, family="binomial")

# print raw results of regression
summary(me31f)
rocResult(me31f)
auc$me31f$formula <- as.character(me31f$call)[2]
auc$me31f$auc <- aucResult(me31f)
```

# Hospital Stay Factors
## Elix Sum, Dispo
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Dispo
- SES: none

```{r MEmodel32}
me32 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + disp, data=train, family="binomial")

# print raw results of regression
summary(me32)
rocResult(me32)
auc$me32$formula <- as.character(me32$call)[2]
auc$me32$auc <- aucResult(me32)
```

## Elix Sum, HoodZscore, Dispo
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Dispo
- SES: Diez-Roux, EthWhite

```{r MEmodel33}
me33 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + disp, data=train, family="binomial") 

# print raw results of regression
summary(me33)
rocResult(me33)
auc$me33$formula <- as.character(me33$call)[2]
auc$me33$auc <- aucResult(me33)
```

## Elix Sum, Payer
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Payer Category
- SES: none

```{r MEmodel34}
me34 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + pay_cat, data=train, family="binomial")

# print raw results of regression
summary(me34)
rocResult(me34)
auc$me34$formula <- as.character(me34$call)[2]
auc$me34$auc <- aucResult(me34)
```

## Elix Sum, HoodZscore, Payer
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Payer Category
- SES: Diez-Roux, EthWhite


```{r MEmodel35}
me35 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + pay_cat, data=train, family="binomial") 

# print raw results of regression
summary(me35)
rocResult(me35)
auc$me35$formula <- as.character(me35$call)[2]
auc$me35$auc <- aucResult(me35)
```

## Elix Sum, Dispo and Payer
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Dispo, Payer
- SES: none

```{r MEmodel36}
me36 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + disp + pay_cat, data=train, family="binomial")

# print raw results of regression
summary(me36)
rocResult(me36)
auc$me36$formula <- as.character(me36$call)[2]
auc$me36$auc <- aucResult(me36)
```

## Elix Sum, HoodZscore, Dispo and Payer
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, Dispo, Payer
- SES: Diez-Roux, EthWhite

```{r MEmodel37}
me37 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + disp + pay_cat, data=train, family="binomial") 

# print raw results of regression
summary(me37)
rocResult(me37)
auc$me37$formula <- as.character(me37$call)[2]
auc$me37$auc <- aucResult(me37)
```

## Elix Sum, LOS
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, LOS
- SES: none

```{r MEmodel38}
me38 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + los, data=train, family="binomial") 

# print raw results of regression
summary(me38)
rocResult(me38)
auc$me38$formula <- as.character(me38$call)[2]
auc$me38$auc <- aucResult(me38)
```

## Elix Sum, LOS, HoodZscore
- Outcome: 30 day readmission from date discharge date after index admission
- Predictors: age (10yrs), sex, Elixhauser Sum, LOS
- SES: Hood Zscore, Ethnicity (% White)

```{r MEmodel39}
me39 <- glm(isreadmit30dc ~ agyradmcentered + sex + elixsum + hoodzscore + ethwhite + los, data=train, family="binomial") 

# print raw results of regression
summary(me39)
rocResult(me39)
auc$me39$formula <- as.character(me39$call)[2]
auc$me39$auc <- aucResult(me39)

```

```{r, cache=F}
# Misc Code
# Calculate confidence intervals and odds ratios for log fixed effects models
# kable(exp(cbind(OR = coef(m2), confint(m2))))

# Calculate confidence intervals and odds ratios for mixed effects models
# me8ci <- confint(me8, parm = "beta_")
# kable(exp(cbind(OR=fixef(me5))))

###

# test/training back to overall 75/25 or per hospital level?


# interaction with comorbidity
# O/E for each specific hospital
# break up hospitals into quintiles
# train model in top volume quintile, apply to all hospitals or lower quintiles

# cluster on volume quintile?!


# designation as a safety net hospital? (categorical)
# number of residents? 
# academic yes/no based on number of residents
# proportion of residents to average daily census?!



# maybe no need to use hospital as random effect because 
# auc relative values 

# round(prop.table(table(ptgu$disp, ptgu$cohort),2)*100,2)
auc <- as.data.frame(do.call(rbind, auc))
datatable(auc)
```
