---
title: "Risk Adjusted Outcomes for Urologic Oncology"
author: "Anobel Y Odisho, John L Gore"
date: "`r Sys.Date()`"
output: 
  tufterhandout::html_tufte_handout:
        theme: cosmo
        css: floating.css
        toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width=12, cache=F)
```
<!--- this inline CSS style is to alter horizontal table padding for stargazer tables -->
<style>
td {
  padding-left: 3px;
  padding-right: 3px;
  }
</style>

```{r}
library(reshape2)
library(stringr)
library(ggplot2)
library(ggthemes)
library(RColorBrewer)
library(knitr)
library(stargazer)
library(DT)
library(leaflet)
library(sparkline)
library(dplyr)
```

```{r load}
dsh <- read.csv("data/tidy/dsh.csv")
zcta <- read.csv("data/tidy/zcta.csv")
acs <- read.csv("data/tidy/acs.csv")
ru <- read.csv("data/tidy/rural.csv")

bg <- "#FCFCFA"
main1 <- "#ca0020"
acc1 <- "#f4a582"
main2 <- "#92c5de"
acc2 <- "#0571b0"

# this function takes arguments x=value, y=number of sig figs, prints mean +/- SD in html
prettyMeanSD <- function (x,y) {
  mean <- prettyNum(round(mean(x, na.rm=TRUE),y), big.mark = ",")
  sd <-  prettyNum(round(sd(x, na.rm=TRUE),y), big.mark = ",")
  paste(mean, " &plusmn; ",sd,sep="")
}

prettyMedianIQR <- function (x,y) {
  median <- prettyNum(round(median(x, na.rm=TRUE),y), big.mark = ",")
  tiles <- round(quantile(x, c(.25, .75), na.rm=TRUE),y)
  paste(median, " (",tiles[1], " - ", tiles[2], ")",sep="")
}
```

# Data Sources
* [Area Health Resource File](http://ahrf.hrsa.gov)
* [Medicare Disproportionate Share Index](https://www.cms.gov/Medicare/Medicare-Fee-for-Service-Payment/AcuteInpatientPPS/Historical-Impact-Files-for-FY-1994-through-Present.html)
* [Medicare General Hospital Data](https://data.medicare.gov/Hospital-Compare/Hospital-General-Information/xubh-q36u)
* [American Community Survey - US Census Bureau](https://www.census.gov/programs-surveys/acs/)
* [Rural Urban Commuting Area Codes: USDA Economic Research Service](http://www.ers.usda.gov/data-products/rural-urban-commuting-area-codes.aspx)
* [Zip Code/ZCTA Crosswalk](https://www.google.com/#safe=off&q=site%3Audsmapper.org%2Fdocs%20-filetype%3Apdf), [Bureau of Primary Health Care, HRSA, DHHS](http://bphc.hrsa.gov/), [Uniform Data System](http://www.udsmapper.org)
* [Boundary Shapefiles: US TIGER/Line](https://www.census.gov/geo/maps-data/data/tiger-line.html)

# DSH Descriptive Analyses
* Total number of hospitals: `r length(unique(dsh$providerid))`
* Years: `r min(dsh$year)` - `r max(dsh$year)`
* Beds per hospital
    + Mean (SD): `r prettyMeanSD(dsh$beds,2)`
    + Median (IQR): `r prettyMedianIQR(dsh$beds)`
    + Is the number of beds per hospital normally distributed? Kolmogorov-Smirnov p-value `r format.pval(ks.test(dsh$beds, pnorm, mean(dsh$beds, na.rm=TRUE), sd(dsh$beds, na.rm=TRUE))$p.value, eps=.001) `

```{r beds.histogram}
ggplot(dsh, aes(x=beds)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white") + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(dsh$beds), sd=sd(dsh$beds))) + 
  geom_density(aes(y=..density..), color=acc2) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Hospitals (density)", x="Number of Hospital Beds")
```


```{r beds.annual.boxplot}
ggplot(dsh, aes(dsh$year, beds)) +
  geom_boxplot(aes(fill=as.factor(dsh$year))) + 
  geom_smooth(aes(group=1), method="lm", se=F, color="black") + 
  scale_fill_brewer(palette="RdBu") +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Beds per Hospital by Year", x="", y="Number of Beds")
```

```{r beds.annual.table, results="asis"}
dsh.t <- dsh %>%
  group_by(year) %>%
  dplyr::summarise(
    Mean = round(mean(beds, na.rm=T),2),
    SD = round(sd(beds, na.rm=T),2)
  )
stargazer(dsh.t, summary = F, type="html", rownames = F)
```

```{r beds.county.boxplot}
dsh %>% filter(!is.na(County.Name)) %>%
ggplot(aes(x=reorder(County.Name, -beds, FUN=median), beds)) +
  geom_boxplot(aes(fill=as.factor(County.Name)), fill=acc2, color=bg) + 
  coord_flip()+
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Beds per Hospital, 2011", x="County", y="Beds per Hospital")
```

* Average Daily Census per hospital
    + Mean (SD): `r prettyMeanSD(dsh$adc,2)`
    + Median (IQR): `r prettyMedianIQR(dsh$adc,2)`
    + Is the average daily census normally distributed? Kolmogorov-Smirnov p-value `r format.pval(ks.test(dsh$adc, pnorm, mean(dsh$adc, na.rm=TRUE), sd(dsh$adc, na.rm=TRUE))$p.value, eps=.001) `

```{r adc.histogram}
ggplot(dsh, aes(x=adc)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white", binwidth=10) + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(dsh$adc, na.rm=TRUE), sd=sd(dsh$adc, na.rm=TRUE))) +
  geom_density(aes(y=..density..), color=acc2) +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Hospitals (density)", x="Average Daily Census")
```

```{r adc.annual.boxplot}
ggplot(dsh, aes(dsh$year, adc)) +
  geom_boxplot(aes(fill=as.factor(dsh$year))) + 
  geom_smooth(aes(group=1), method="lm", se=F, color="black") + 
  scale_fill_brewer(palette="RdBu") +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Average Daily Census per Hospital by Year", x="", y="Average Daily Census")
```

```{r adc.annual.table, results="asis"}
dsh.t <- dsh %>%
  group_by(year) %>%
  dplyr::summarise(
    Mean = round(mean(adc, na.rm=T),2),
    SD = round(sd(adc, na.rm=T),2)
  )
stargazer(dsh.t, summary = F, type="html", rownames = F)
```

```{r adc.county.boxplot}
dsh %>% filter(!is.na(County.Name)) %>%
ggplot(aes(x=reorder(County.Name, adc, FUN=median), adc)) +
  geom_boxplot(aes(fill=as.factor(County.Name)), fill=acc2, color=bg) + 
  coord_flip()+
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Average Daily Census per Hospital, 2011", x="County", y="Average Daily Census")
```

* DSH Percentage Distribution
    + Mean (SD): `r prettyMeanSD(dsh$dsh_pct,2)`%
    + Median (IQR): `r prettyMedianIQR(dsh$dsh_pct,2)`%
    + Is the DSH percentage per hospital normally distributed? Kolmogorov-Smirnov p-value `r format.pval(ks.test(dsh$dsh_pct, pnorm, mean(dsh$dsh_pct, na.rm=TRUE), sd(dsh$dsh_pct, na.rm=TRUE))$p.value, eps=.001) `

```{r dsh.histogram}
ggplot(dsh, aes(x=dsh_pct)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white") + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(dsh$dsh_pct), sd=sd(dsh$dsh_pct))) + 
  geom_density(aes(y=..density..), color=acc2) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Hospitals (density)", x="Medicare DSH Percentage")
```

```{r dsh.annual.boxplot}
ggplot(dsh, aes(dsh$year, dsh_pct)) +
  geom_boxplot(aes(fill=as.factor(dsh$year))) + 
  geom_smooth(aes(group=1), method="lm", se=F, color="black") + 
  scale_fill_brewer(palette="RdBu") +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="DSH per hospital by year", x="", y="DSH")
```

```{r dsh.annual.table, results="asis"}
dsh.t <- dsh %>%
  group_by(year) %>%
  dplyr::summarise(
    Mean = round(mean(dsh_pct, na.rm=T),2),
    SD = round(sd(dsh_pct, na.rm=T),2)
  )
stargazer(dsh.t, summary = F, type="html", rownames = F)
```

```{r dsh.county.boxplot}
dsh %>% filter(!is.na(County.Name)) %>%
ggplot(aes(x=reorder(County.Name, -dsh_pct, FUN=median), dsh_pct)) +
  geom_boxplot(aes(fill=as.factor(County.Name)), fill=acc2, color=bg) + 
  coord_flip()+
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="DSH Index per Hospital by County, 2011", x="County", y="DSH %")
```

* Medicare Percentage Distribution
    + Mean (SD): `r prettyMeanSD(dsh$mcr_pct,2)`%
    + Median (IQR): `r prettyMedianIQR(dsh$mcr_pct,2)`%
    + Is the DSH percentage per hospital normally distributed? Kolmogorov-Smirnov p-value `r format.pval(ks.test(dsh$mcr_pct, pnorm, mean(dsh$mcr_pct, na.rm=TRUE), sd(dsh$mcr_pct, na.rm=TRUE))$p.value, eps=.001) `

```{r mcr.histogram}
ggplot(dsh, aes(x=mcr_pct)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white") + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(dsh$mcr_pct, na.rm=TRUE), sd=sd(dsh$mcr_pct, na.rm=TRUE))) + 
  geom_density(aes(y=..density..), color=acc2) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Hospitals (density)", x="Medicare Patient Percentage")
```

```{r mcr_pct.annual.boxplot}
ggplot(dsh, aes(dsh$year, mcr_pct)) +
  geom_boxplot(aes(fill=as.factor(dsh$year))) + 
  geom_smooth(aes(group=1), method="lm", se=F, color="black") + 
  scale_fill_brewer(palette="RdBu") +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="% of Medicare Patients per hospital by year", x="", y="Medicare Percentage")
```

```{r mcr_pct.annual.table, results="asis"}
dsh.t <- dsh %>%
  group_by(year) %>%
  dplyr::summarise(
    Mean = round(mean(mcr_pct, na.rm=T),2),
    SD = round(sd(mcr_pct, na.rm=T),2)
  )
stargazer(dsh.t, summary = F, type="html", rownames = F)
```

```{r mcr_pct.county.boxplot}
dsh %>% filter(!is.na(County.Name)) %>%
ggplot(aes(x=reorder(County.Name, mcr_pct, FUN=median), mcr_pct)) +
  geom_boxplot(aes(fill=as.factor(County.Name)), fill=acc2, color=bg) + 
  coord_flip()+
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="% Medicare Patientsper Hospital by County", x="County", y="% Medicare Patients")
```

* Case Mix Index Adjustment
    + Mean (SD): `r prettyMeanSD(dsh$cmi,2)`%
    + Median (IQR): `r prettyMedianIQR(dsh$cmi,2)`%
    + Is the DSH percentage per hospital normally distributed? Kolmogorov-Smirnov p-value `r format.pval(ks.test(dsh$cmi, pnorm, mean(dsh$cmi, na.rm=TRUE), sd(dsh$cmi, na.rm=TRUE))$p.value, eps=.001) `

```{r cmi.histogram}
ggplot(dsh, aes(x=cmi)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white") + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(dsh$cmi, na.rm=TRUE), sd=sd(dsh$cmi, na.rm=TRUE))) + 
  geom_density(aes(y=..density..), color=acc2) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Hospitals (density)", x="Case Mix Index")
```

```{r cmi.annual.boxplot}
ggplot(dsh, aes(dsh$year, cmi)) +
  geom_boxplot(aes(fill=as.factor(dsh$year))) + 
  geom_smooth(aes(group=1), method="lm", se=F, color="black") + 
  scale_fill_brewer(palette="RdBu") +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Case Mix Index by Year", x="", y="Case Mix Index")
```

```{r cmi.annual.table, results="asis"}
dsh.t <- dsh %>%
  group_by(year) %>%
  dplyr::summarise(
    Mean = round(mean(cmi, na.rm=T),2),
    SD = round(sd(cmi, na.rm=T),2)
  )

stargazer(dsh.t, summary = F, type="html", rownames = F)
```

```{r cmi.county.boxplot}
dsh %>% filter(!is.na(County.Name)) %>%
ggplot(aes(x=reorder(County.Name, -cmi, FUN=median), cmi)) +
  geom_boxplot(aes(fill=as.factor(County.Name)), fill=acc2, color=bg) + 
  coord_flip()+
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.position="none") +
  labs(title="Case Mix Index by County", x="County", y="Case Mix Index")
```

# Map of CA Hospitals
Represents map of hospitals, based on Medicare DSH data and Medicare Hospital Info  
Select individual points for more details.
```{r hospital.map, cache=F}
dsh2011 <- filter(dsh, year=="2011")

popup <- data.frame(
  title=paste("<b>",str_to_title(dsh2011$name),"</b>"),
  beds = paste("Beds:", dsh2011$beds),
  adc = paste("Average Daily Census:", dsh2011$adc),
  dsh_pct = paste("Medicare DSH:", round(dsh2011$dsh_pct,2), "%"),
  mcr_pct = paste("Medicare Patients:", round(dsh2011$mcr_pct,2), "%")
)
popup <- apply(popup, 1, FUN=paste, collapse="</br>")

m <-  leaflet(dsh2011) %>%
  addTiles('http://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}.png') %>%
    addCircleMarkers(lat=dsh2011$lat, lng=dsh2011$lon, color=main1,clusterOptions = markerClusterOptions(), popup=popup)

m
```

# RUCA Codes
RUCA Code | Description
----------|------------
1|Metropolitan area core: primary flow within an urbanized area (UA)
2|Metropolitan area high commuting: primary flow 30% or more to a UA
3|Metropolitan area low commuting: primary flow 10% to 30% to a UA
4|Micropolitan area core: primary flow within an Urban Cluster of 10,000 to 49,999 (large UC)
5|Micropolitan high commuting: primary flow 30% or more to a large UC
6|Micropolitan low commuting: primary flow 10% to 30% to a large UC
7|Small town core: primary flow within an Urban Cluster of 2,500 to 9,999 (small UC)
8|Small town high commuting: primary flow 30% or more to a small UC
9|Small town low commuting: primary flow 10% to 30% to a small UC
10|Rural areas: primary flow to a tract outside a UA or UC

``` {r ruca.hist, cache=FALSE}
ggplot(ru, aes(x=ruca)) + 
  geom_histogram(fill=main2, color="white", binwidth=1, origin = -0.5) + 
  scale_x_continuous(breaks=1:10) +
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="Number of ZCTAs", x="RUCA")
```

# ACS Data
``` {r acs.map, cache=FALSE, fig.height=16}
maps$overall
```

# MD Distribution
``` {r allmddistribution, cache=FALSE, fig.height=16}
maps$density
```

# Neighborhood Z-Scores
``` {r z.scores.hist}
ggplot(acsz, aes(x=hoodzscore)) + 
  geom_histogram(aes(y=..density..), fill=main2, color="white") + 
  stat_function(fun=dnorm, color="indianred4", arg=list(mean=mean(acsz$hoodzscore, na.rm=T), sd=sd(acsz$hoodzscore, na.rm=T))) + 
  geom_density(aes(y=..density..), color=acc2) + 
  theme_few() +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg), legend.title=element_blank()) + 
  labs(y="ZCTAs", x="Diez-Roux Neighborhood Z-Score")
```