---
title: "Risk Adjusted Outcomes for Urologic Oncology"
subtitle: "O/E Evaluation"
author: "Anobel Y Odisho, Ruth Etzioni, John L Gore"
date: "`r Sys.Date()`"
output: 
  tufterhandout::html_tufte_handout:
        theme: cosmo
        css: floating.css
        toc: yes
params:
    cohort: ""
---

  
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width=12, cache=F)
```

<!--- this inline CSS style is to alter horizontal table padding for stargazer tables -->
  <style>
  td {
    padding-left: 3px;
    padding-right: 3px;
  }
</style>
  
```{r packages, cache=F}
# Data Cleaning Packages
library(dplyr)      # Data Management
library(tidyr)      # Data Cleaning
library(stringr)    # String manipulation

# Graphics Packages
library(ggplot2)    # Graphics
library(ggthemes)   # Themes for ggplot
library(DT)         # HTML Widget for Data Tables
library(stargazer)  # HTML Tables for regression results
library(knitr)
library(RColorBrewer)# Color palettes from Cynthia Brewer

# Specialty/Stats Packages
library(ROCR)       # Performance measures, ROC curves, AUC
library(lme4)       # Mixed Effects Models
library(coin)       # Permutation Testing
```

```{r constants.functions, cache=F}
bg <- "#FCFCFA"
main1 <- "#ca0020"
acc1 <- "#f4a582"
main2 <- "#92c5de"
acc2 <- "#0571b0"

resPairsTable <- function(x) {
  matsize <- length(grep("p_", names(pred)))
  p <- lapply(1:length(x), function(y) format.pval(x[[y]]$p.value, eps = 0.001, digits=3))
  ptable <- diag(matsize)
  ptable[lower.tri(ptable, diag=F)] <- p
  t(ptable)
  ptable <- matrix(ptable, nrow=matsize, ncol=matsize, byrow=T)
  rownames(ptable) = grep("p_", names(pred), value=T)
  colnames(ptable) = grep("p_", names(pred), value=T)
  ptable[ptable==0] <- ""
  ptable[ptable==1] <- ""
  return(kable(ptable))
}

## Function to generate table of permutation testing p-values
resPermsTable <- function(x, nummodels) {
  matsize <- nummodels+1
  p <- lapply(x, pvalue)
  p <- lapply(p, function(y) format.pval(y, eps = 0.001, digits=3))
  ptable <- diag(matsize)
  ptable[lower.tri(ptable, diag=F)] <- p
  t(ptable)
  ptable <- matrix(ptable, nrow=matsize, ncol=matsize, byrow=T)  
  rownames(ptable) = grep("^r_", names(pred), value=T)
  colnames(ptable) = grep("^r_", names(pred), value=T)
  ptable[ptable==0] <- ""
  ptable[ptable==1] <- ""
  return(kable(ptable))
}

# function to calculate all possible combinations of ranks
comboDiffs <- function(x) {
  df <- lapply(seq_along(combinations), function (y) {
    pred <- pred[pred$cohort==x,colnames(pred) %in% unlist(combinations[y])]
    result <- unlist(pred[,1])-unlist(pred[,2])
    return(result)
  }) 
  names(df) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = "_vs_")
  df <- as.data.frame(df)
  df$cohort <- x
  return(df)
}

```

```{r loaddata}
# Import data, keep only Cystectomy, Partial Nephrectomy, and Radical Nephrectomy cohorts
# exclude hospitals with only 1 observation
# drop patients with missing zip codes
ptgu <- readRDS("data/patient/tidy/ptgu.rds") %>%
  filter(cohort %in% c("Cystectomy", "PartialNx", "RadNx")) %>%
  group_by(cohort, oshpd_id) %>%
  filter(n()>1) %>%
  filter(!is.na(patzcta))

# List variables that will be scaled for models
toscale <- c("agyradmcentered", "agyradm",
             "elixsum", 
             "bedsMean", "adcMean", "dsh_pctMean", "mcr_pctMean", "cmiMean",
             "ethwhite", "ethblack", "ethlatin", "ethasian", "ethother",
             "medianincome", "capincome", "housevalue",
             "edunohs",	"eduhs", "educollege", "empexec",
             "gini", "iceinc", "iceedu", "iceeth", "hoodzscore", 
             "km", "hours", 
             "los", "cohortmortality", "residentnum")

# scale and center variables
ptgu[,toscale] <- data.frame(lapply(ptgu[,toscale], scale, center=T, scale=T))
rm(toscale)

# split data into training and validation cohorts
# Set random seed to reproduce results
set.seed(7)

# create an index variable which will allow splitting of training/test data without overlap
ptgu$index <- seq(1:nrow(ptgu))

# Group by OSHPD_ID and cohort, then take a 75% sample for training set
train <- ptgu %>%
  group_by(cohort, oshpd_id) %>%
  sample_frac(size=0.75, replace=F)

# anything that didnt make it into training set is put into a test set
test <- ptgu[!(ptgu$index %in% train$index),]

# remove index variables
ptgu <- ptgu %>% select(-index)
train <- train %>% select(-index)
test <- test %>% select(-index)
```

```{r observedrankings}
# Calculate observed hospital level readmission rates and rankings, per cohort
ranks <- test %>%
  group_by(cohort, oshpd_id) %>%
  summarise(
    cases = n(),
    p_obs = sum(isreadmit30dc)/n()
  ) %>%
  # filter(cases>4) %>%
  mutate(
    r_obs = rank(p_obs, ties.method="average"))

ranks <- test %>% 
  group_by(oshpd_id) %>%
  select(oshpd_id, safetydsh, safetynaph, safetydsh4, safetydsh10) %>%
  distinct() %>%
  right_join(ranks)

ranks %>%
  group_by("Cohort" = cohort) %>%
  summarise(
    "Number of Hospitals in Test Data" = n()
  ) %>% kable()

ranks %>%
  group_by("Cohort" = cohort, "Safety Net Status" = safetydsh4) %>%
  summarise(
    "Number of Hospitals in Test Data" = n()
  ) %>% kable()
```

# Combined Models

- Base Model: Age, Sex, Elixhauser Sum
- Base with SES: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity
- Base with SES + RU: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity
- Base with Hospital Factors: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity
- Base with Hospital Factors + SES: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity
- Base with Hospital Factors + SES + Rural: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity

P-values represent two sided Wilcoxon Rank Sum tests comparing rankings of predicted probabilites at the hospital level in non-SES models to models incoporating SES.

```{r combinedmodels}
results <- train %>%
  group_by(cohort) %>%
  do(
    "p_base" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum, data=., family="binomial"),
    "p_base_ses" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum + hoodzscore + ethwhite, data=., family="binomial"),
    "p_base_sesru" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum + hoodzscore + ethwhite + ru + km, data=., family="binomial"),
    "p_hospfactors" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum + volumequint + bedsMean + residency, data=., family="binomial"),
    "p_hospfactors_ses" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum + volumequint + bedsMean + residency + hoodzscore + ethwhite, data=., family="binomial"),
    "p_hospfactors_sesru" = glm(isreadmit30dc ~ agyradm + sex + open + elixsum + volumequint + bedsMean + residency + hoodzscore + ethwhite + ru + km, data=., family="binomial")
  )

# Assign number of cohorts and number of models (for later use)
numcohorts <- length(unique(test$cohort))
nummodels <- ncol(results)-1
```

``` {r predictedprobs_combinedmodels}
# Generate predicted probabilities for admission
# index <- lapply(1:numcohorts, function(x) seq(numcohorts+x,(nummodels+1)*numcohorts, by=numcohorts))

# results <- unlist(results)
# results <- lapply(index, function(x) results[x])
prednames <- colnames(results)[-1]
results <- t(results)

pred_cystectomy <- as.data.frame(lapply(2:nrow(results), function(x) predict(results[[x,1]], newdata=test[test$cohort=="Cystectomy",], type="response")))

pred_partialnx <- as.data.frame(lapply(2:nrow(results), function(x) predict(results[[x,2]], newdata=test[test$cohort=="PartialNx",], type="response")))

pred_radnx <- as.data.frame(lapply(2:nrow(results), function(x) predict(results[[x,3]], newdata=test[test$cohort=="RadNx",], type="response")))

colnames(pred_cystectomy) <- prednames
colnames(pred_partialnx) <- prednames
colnames(pred_radnx) <- prednames

pred_cystectomy <- cbind(test[test$cohort=="Cystectomy",], pred_cystectomy)
pred_partialnx <- cbind(test[test$cohort=="PartialNx",], pred_partialnx)
pred_radnx <- cbind(test[test$cohort=="RadNx",], pred_radnx)

# names(pred_cystectomy) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_cystectomy))
# names(pred_partialnx) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_partialnx))
# names(pred_radnx) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_radnx))

pred_all <- rbind(pred_cystectomy, pred_partialnx, pred_radnx)
rm(pred_cystectomy, pred_partialnx, pred_radnx)

# extract names of columns for predicted probabilities
vars <- grep("p_", names(pred_all), value=T)
# replace the "p_" with "r_" to start the name, use it in the mutate_each_() function
vars_r <- setNames(vars, str_replace(vars, "p_", "r_"))

# calculate assign cohort/hospital specific predicted probabilities, then rank by cohort
pred <- pred_all %>%
  group_by(cohort, oshpd_id) %>%
  summarise_each(funs(mean), starts_with("p_")) %>%
  group_by(cohort) %>%
  mutate_each_(funs(rank(., ties.method="average")), vars_r) %>%
  right_join(ranks)

res_probs <- pred %>%
  select(-safetynaph, -safetydsh, -safetydsh10, -cases, -oshpd_id) %>%
  group_by(cohort, safetydsh4) %>%
  summarise_each(funs(mean(., na.rm=T)))%>%
  mutate_each(funs(.*100), matches("p_|pct_")) %>%
  group_by(cohort, safetydsh4) %>%
  mutate_each(funs(sprintf("%.2f", .)))%>% 
  t() %>% as.data.frame()

res_names <- paste(unlist(res_probs[1,]), unlist(res_probs[2,]))
res_names <- str_replace_all(res_names, "FALSE", "Not SHN")
res_names <- str_replace_all(res_names, "TRUE", "SHN")
colnames(res_probs) <- res_names
res_probs <- res_probs[3:nrow(res_probs),]
rm(res_names)

# arrange by row names (all model probabilities first, then rankings)
res_probs <- res_probs[order(row.names(res_probs)),]

kable(res_probs)
```

## Differences in Overall Rankings
p-values from Two Sample Wilcoxon Signed Rank Test (Mann-Whitney), comparing predicted probabilities of readmission in each of the pairwise combinations of models. A significant p-value indicates that the hospital rankings, based on predicted probabilities generated by each model, are different from the comparator model. 
All pairwise combinations are assessed for each cohort.

```{r}
# Rearrange columns to make p_obs first
pred <- pred %>%
  select(p_obs, starts_with("p_"), r_obs, starts_with("r_"), everything())

combinations <- combn(grep("p_", names(pred), value=T),2, simplify = F)

res_pairs_cystectomy <- lapply(seq_along(combinations), function (x) {
  pred <- pred[pred$cohort=="Cystectomy",colnames(pred) %in% unlist(combinations[x])]
  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
  return(result)
})

res_pairs_partialnx <- lapply(seq_along(combinations), function (x) {
  pred <- pred[pred$cohort=="PartialNx",colnames(pred) %in% unlist(combinations[x])]
  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
  return(result)
})

res_pairs_radnx <- lapply(seq_along(combinations), function (x) {
  pred <- pred[pred$cohort=="RadNx",colnames(pred) %in% unlist(combinations[x])]
  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
  return(result)
})

# Rename list for legibility    
names(res_pairs_cystectomy) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")

names(res_pairs_partialnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")

names(res_pairs_radnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")
```

### Cystectomy
```{r}
resPairsTable(res_pairs_cystectomy)
```

### Partial Nephrectomy
```{r}
resPairsTable(res_pairs_partialnx)
```

### Radical Nephrectomy
```{r}
resPairsTable(res_pairs_radnx)
```

## Changes in Expected Rankings
### SHN vs Non-SHN

Is the change in rank different between Safety Net and Non-Safety Net Hospitals?
We calculated the change in rank based on predicted probabilities from each model, and performed all pairwise comparisons. No assumptions about the distribution in differences was made, and a permutation test was performed comparing SHN to non-SHN hospitals. 

```{r}
# generate all possible combinations of ranks
combinations <- combn(grep("^r_", names(pred), value=T),2, simplify = F)

perms <- lapply(unique(pred$cohort), comboDiffs)
perms <- rbind_all(perms)

perms <- cbind(perms, "safetydsh4" = factor(ifelse(pred$safetydsh4, "Yes", "No")))

res_perm_cystectomy <- lapply(grep("^r_", colnames(perms)), function (x) {
  independence_test(perms[perms$cohort=="Cystectomy",x] ~ safetydsh4, data=perms[perms$cohort=="Cystectomy",], ytrafo=rank_trafo, distribution=exact())
})

res_perm_partialnx <- lapply(grep("^r_", colnames(perms)), function (x) {
  independence_test(perms[perms$cohort=="PartialNx",x] ~ safetydsh4, data=perms[perms$cohort=="PartialNx",], ytrafo=rank_trafo, distribution=exact())
})

res_perm_radnx <- lapply(grep("^r_", colnames(perms)), function (x) {
  independence_test(perms[perms$cohort=="RadNx",x] ~ safetydsh4, data=perms[perms$cohort=="RadNx",], ytrafo=rank_trafo, distribution=exact())
})

names(res_perm_cystectomy) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = "_vs_")

names(res_perm_partialnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = "_vs_")

names(res_perm_radnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = "_vs_")
```

### Cystectomy
```{r}
resPermsTable(res_perm_cystectomy, nummodels)
```

### Partial Nephrectomy
```{r}
resPermsTable(res_perm_partialnx, nummodels)
```

### Radical Nephrectomy
```{r}
resPermsTable(res_perm_radnx, nummodels)
```


```{r rankingfigs, eval=F}
# 30d Readmissions for cystectomy by safety net status
pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_obs), y=100*p_obs+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Observed 30 Day Readmission Rate for Cystectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_base), y=100*p_base+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Predicted 30 Day Readmission Rate for Cystectomy by Safety Net Status (Base Model)", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_base_ses), y=100*p_base_ses+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Predicted 30 Day Readmission Rate for Cystectomy by Safety Net Status (Base + SES)", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_base_sesru), y=100*p_base_sesru+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Predicted 30 Day Readmission Rate for Cystectomy by Safety Net Status (Base + SES + Rural)", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

# 30d Readmissions for Partial Nephrectomy by safety net status
pred %>% filter(cohort=="PartialNx" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_base), y=100*p_base+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="30 Day Readmission Rate for Partial Nephrectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

# 30d Readmissions for Radical Nephrectomy by safety net status
pred %>% filter(cohort=="RadNx" & !is.na(safetydsh4)) %>%
  ggplot(aes(x=reorder(oshpd_id, -p_base_ses), y=100*p_base_ses+.5, fill=safetydsh4)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="30 Day Readmission Rate for Radical Nephrectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))
```

```{r eval=F}
ranks %>%
  filter(cohort=="Cystectomy") %>%
  filter(safetydsh==T) %>%
  select(oshpd_id, r_obs, r_base, r_base_ses) %>%
  arrange(desc(r_base_ses)) %>%
  write.csv("temp.csv")
```