---
title: "Risk Adjusted Outcomes for Urologic Oncology"
subtitle: "O/E Evaluation"
author: "Anobel Y Odisho, Ruth Etzioni, John L Gore"
date: "`r Sys.Date()`"
output: 
  tufterhandout::html_tufte_handout:
        theme: cosmo
        css: floating.css
        toc: yes
params:
    cohort: ""
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width=12, cache=F)
```

<!--- this inline CSS style is to alter horizontal table padding for stargazer tables -->
<style>
  td {
    padding-left: 3px;
    padding-right: 3px;
  }
</style>
  
```{r packages, cache=F}
# Data Cleaning Packages
library(dplyr)
library(stringr)
library(tidyr)

# Graphics Packages
library(DT)
library(ggplot2)
library(ggthemes)
library(knitr)
library(RColorBrewer)
library(stargazer)

# Specialty/Stats Packages
library(ROCR)
library(lme4)
```

```{r constants.functions, cache=F}
bg <- "#FCFCFA"
main1 <- "#ca0020"
acc1 <- "#f4a582"
main2 <- "#92c5de"
acc2 <- "#0571b0"

resPairsTable <- function(x) {
  matsize <- length(grep("p_", names(pred)))
  p <- lapply(1:length(x), function(y) format.pval(x[[y]]$p.value, eps = 0.001, digits=3))
  ptable <- diag(matsize)
  ptable[lower.tri(ptable, diag=F)] <- p
  t(ptable)
  ptable <- matrix(ptable, nrow=matsize, ncol=matsize, byrow=T)
  rownames(ptable) = grep("p_", names(pred), value=T)
  colnames(ptable) = grep("p_", names(pred), value=T)
  ptable[ptable==0] <- ""
  ptable[ptable==1] <- ""
  return(kable(ptable))
  }
```

```{r loaddata}
# Import data, keep only Cystectomy, Partial Nephrectomy, and Radical Nephrectomy cohorts
# exclude hospitals with only 1 observation
ptgu <- readRDS("rao_workingdata/ptgu.rds") %>%
  filter(cohort %in% c("Cystectomy", "PartialNx", "RadNx")) %>%
  group_by(cohort, oshpd_id) %>%
  filter(n()>1)

# List variables that will be scaled for models
toscale <- c("agyradmcentered", "agyradm",
             "elixsum", 
             "bedsMean", "adcMean", "dsh_pctMean", "mcr_pctMean", "cmiMean",
             "ethwhite", "ethblack", "ethlatin", "ethasian", "ethother",
             "medianincome", "capincome", "housevalue",
             "edunohs",	"eduhs", "educollege", "empexec",
             "gini", "iceinc", "iceedu", "iceeth", "hoodzscore", 
             "km", "hours", 
             "los", "cohortmortality", "residentnum")

# scale and center variables
ptgu[,toscale] <- data.frame(lapply(ptgu[,toscale], scale, center=T, scale=T))
rm(toscale)

# split data into training and validation cohorts
# Set random seed to reproduce results
set.seed(7)

# create an index variable which will allow splitting of training/test data without overlap
ptgu$index <- seq(1:nrow(ptgu))

# Group by OSHPD_ID and cohort, then take a 75% sample for training set
train <- ptgu %>%
  group_by(cohort, oshpd_id) %>%
  
  sample_frac(size=0.75, replace=F)
# anything that didnt make it into training set is put into a test set
test <- ptgu[!(ptgu$index %in% train$index),]

# remove index variables
ptgu <- ptgu %>% select(-index)
train <- train %>% select(-index)
test <- test %>% select(-index)
```

```{r observedrankings}
# Calculate observed hospital level readmission rates and rankings, per cohort
ranks <- test %>%
	group_by(cohort, oshpd_id) %>%
	summarise(
		cases = n(),
		p_obs = sum(isreadmit30dc)/n()
		) %>%
	# filter(cases>4) %>%
	mutate(r_obs = rank(p_obs, ties.method="average"))

ranks <- test %>% 
	group_by(oshpd_id, safetydsh, safetynaph) %>%
	select(oshpd_id, safetydsh, safetynaph) %>%
	distinct() %>%
	right_join(ranks)

ranks %>%
  group_by("Cohort" = cohort) %>%
  summarise(
    "Number of Hospitals in Test Data" = n()
  ) %>% kable()
```

# Models
- Base Model: Age, Sex, Elixhauser Sum
- Base with SES: Age, Sex, Elixhauser Sum, Diez-Roux Score, Ethnicity
- more to come here

P-values represent two sided Wilcoxon Rank Sum tests comparing rankings of predicted probabilites at the hospital level in non-SES models to models incoporating SES.

```{r models}
# run models for each cohort
results <- train %>%
  group_by(cohort) %>%
  do(
    "p_base" = glmer(isreadmit30dc ~ agyradm + sex + elixsum + (1|oshpd_id), data=., family="binomial"),
    "p_base_ses" = glmer(isreadmit30dc ~ agyradm + sex + elixsum + hoodzscore + ethwhite + (1|oshpd_id), data=., family="binomial"),
    "p_payer" = glmer(isreadmit30dc ~ agyradm + sex + elixsum + pay_cat + (1|oshpd_id), data=., family="binomial"),
    "p_payer_ses" = glmer(isreadmit30dc ~ agyradm + sex + elixsum + pay_cat + hoodzscore + ethwhite + (1|oshpd_id), data=., family="binomial")
  )
```

``` {r predictedprobs}
numcohorts <- length(unique(ptgu$cohort))
nummodels <- ncol(results)-1

# Generate predicted probabilities for admission
index <- lapply(1:numcohorts, function(x) seq(numcohorts+x,(nummodels+1)*numcohorts, by=numcohorts))

results <- unlist(results)
results <- lapply(index, function(x) results[x])

pred_cystectomy <- as.data.frame(lapply(results[[1]], function(x) predict(x, newdata=test[test$cohort=="Cystectomy",], type="response", allow.new.levels=T)))

pred_partialnx <- as.data.frame(lapply(results[[2]], function(x) predict(x, newdata=test[test$cohort=="PartialNx",], type="response", allow.new.levels=T)))

pred_radnx <- as.data.frame(lapply(results[[3]], function(x) predict(x, newdata=test[test$cohort=="RadNx",], type="response", allow.new.levels=T)))

pred_cystectomy <- cbind(test[test$cohort=="Cystectomy",], pred_cystectomy)
pred_partialnx <- cbind(test[test$cohort=="PartialNx",], pred_partialnx)
pred_radnx <- cbind(test[test$cohort=="RadNx",], pred_radnx)

names(pred_cystectomy) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_cystectomy))
names(pred_partialnx) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_partialnx))
names(pred_radnx) <- gsub("(^p_.+)([0-9])+", "\\1", names(pred_radnx))

pred_all <- rbind(pred_cystectomy, pred_partialnx, pred_radnx)
rm(pred_cystectomy, pred_partialnx, pred_radnx)

pred <- pred_all %>%
  group_by(cohort, oshpd_id) %>%
  summarise(
    p_base = mean(p_base, na.rm=T),
    p_base_ses = mean(p_base_ses, na.rm=T),
    p_payer = mean(p_payer, na.rm=T),
    p_payer_ses = mean(p_payer_ses, na.rm=T)
      ) %>%
  group_by(cohort) %>%
  mutate(
    r_base = rank(p_base, ties.method="average"),
    r_base_ses = rank(p_base_ses, ties.method="average"),
    r_payer = rank(p_payer, ties.method="average"),
    r_payer_ses = rank(p_payer_ses, ties.method="average")
  ) %>%
  right_join(ranks)

res_probs <- pred %>%
filter(!is.na(p_obs)) %>%
  group_by(cohort, safetydsh) %>%
  mutate(
    changerank_base_v_obs = r_base - r_obs,
    changerank_base_ses_v_obs = r_base_ses - r_obs,
    changerank_base_v_base_ses = r_base_ses - r_obs,
    changerank_base_v_payer = r_payer - r_obs,
    changerank_base_v_payer_ses = r_payer_ses - r_obs
  ) %>%
  summarise(
    "Hospitals" = n(),
    "Obs Readmission Rate" = sprintf("%.2f", 100*mean(p_obs, na.rm=T)),
    "Obs Rank" = sprintf("%.1f", mean(r_obs, na.rm=T)),
    "Pred Prob - Base" = sprintf("%.2f", 100*mean(p_base, na.rm=T)),
    "Pred Rank - Base" = sprintf("%.1f", mean(r_base, na.rm=T)),
    "Mean Rank Change - Base" = sprintf("%.2f", mean(changerank_base_v_obs, na.rm=T)),
    "Pred Prob - Base SES" = sprintf("%.2f", 100*mean(p_base_ses, na.rm=T)),
    "Pred Rank - Base SES" = sprintf("%.1f", mean(r_base_ses, na.rm=T)),
    "Mean Rank Change - SES" = sprintf("%.2f", mean(changerank_base_ses_v_obs, na.rm=T))
  ) %>% t() %>% as.data.frame()

res_names <- paste(unlist(res_probs[1,]), unlist(res_probs[2,]))
res_names <- str_replace_all(res_names, "FALSE", "Not SHN")
res_names <- str_replace_all(res_names, "TRUE", "SHN")

colnames(res_probs) <- res_names
res_probs <- res_probs[3:nrow(res_probs),]
rm(res_names)

res_wilcox <- pred %>% 
  filter(!is.na(p_obs)) %>%
  group_by(cohort) %>%
  do(
    "Pred Prob - Base SES" = wilcox.test(.$p_base, .$p_base_ses, paired = T, conf.int = T)$p.value
  ) %>% t() %>% as.data.frame()

res_wilcoxcols <- unlist(res_wilcox[1,])
res_wilcoxrows <- rownames(res_wilcox)[-1]
res_wilcox <- as.data.frame(matrix(unlist(res_wilcox), nrow=nrow(res_wilcox)), stringsAsFactors = F)
res_wilcox <- res_wilcox[-1,]

res_wilcox <- as.data.frame(lapply(res_wilcox, as.numeric))

res_wilcox <- as.data.frame(lapply(res_wilcox, format.pval, eps=0.001, digits=3), stringsAsFactors=F)

colnames(res_wilcox) <- paste0(res_wilcoxcols, " p-value")
res_wilcox$id <- res_wilcoxrows

res_probs$id <- row.names(res_probs)
res <- left_join(res_probs, res_wilcox)
res[is.na(res)] <- ""

rownames(res) <- res$id
res$id <- NULL

res <- res[(sort(colnames(res)))]
rm(res_wilcoxrows, res_wilcoxcols, index)
kable(res)

# newpred %>% filter(cohort=="Cystectomy" & !is.na(safetynaph)) %>%
# ggplot(aes(x=reorder(oshpd_id, -p_base_ses), y=100*p_base_ses, fill=safetynaph)) +
#   geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
#   labs(title="30 Day Readmission Rate for Cystectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
#   scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
#   theme_few() + 
#   theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
#   theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

```

## All Pairwise Combinations
p-values from Two Sample Wilcoxon Signed Rank Test (Mann-Whitney), comparing ranks of predicted probabilities of readmission

```{r}
# Rearrange columns to make p_obs first

pred <- pred %>%
  select(p_obs, starts_with("p_"), r_obs, starts_with("r_"), everything())

combinations <- combn(grep("p_", names(pred), value=T),2, simplify = F)

res_pairs_cystectomy <- lapply(seq_along(combinations), function (x) {
                  pred <- pred[pred$cohort=="Cystectomy",colnames(pred) %in% unlist(combinations[x])]
                  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
                  return(result)
                  })

res_pairs_partialnx <- lapply(seq_along(combinations), function (x) {
                  pred <- pred[pred$cohort=="PartialNx",colnames(pred) %in% unlist(combinations[x])]
                  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
                  return(result)
                  })

res_pairs_radnx <- lapply(seq_along(combinations), function (x) {
                  pred <- pred[pred$cohort=="RadNx",colnames(pred) %in% unlist(combinations[x])]
                  result <- wilcox.test(unlist(pred[,1]), unlist(pred[,2]), paired=T)
                  return(result)
                  })

# Rename list for legibility    
names(res_pairs_cystectomy) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")

names(res_pairs_partialnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")

names(res_pairs_radnx) <- paste(matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,1], matrix(unlist(combinations), ncol = 2, byrow = TRUE)[,2], sep = " vs. ")
```

### Cystectomy
```{r}
resPairsTable(res_pairs_cystectomy)
```

### Partial Nephrectomy
```{r}
resPairsTable(res_pairs_partialnx)
```

### Radical Nephrectomy
```{r}
resPairsTable(res_pairs_radnx)
```

```{r oe, eval=F}
oe <- pred %>%
  group_by(cohort) %>%
  mutate(
    changerank_base_v_obs = r_base - r_obs,
    changerank_base_ses_v_obs = r_base_ses - r_obs,
    changerank_base_v_base_ses = r_base - r_base_ses)

# you want your predicted rank to be WORSE (bigger) than the observed rank
# doing well relative to what is expected
# so r_base - r_obs should be POSITIVE

t.test(changerank_base_v_obs ~ safetydsh, data=oe[oe$cohort=="Cystectomy",])
t.test(changerank_base_ses_v_obs ~ safetydsh, data=oe[oe$cohort=="Cystectomy",])
t.test(changerank_base_v_base_ses ~ safetydsh, data=oe[oe$cohort=="Cystectomy",])


t.test(changerank_base_v_obs ~ safetydsh, data=oe[oe$cohort=="PartialNx",])
t.test(changerank_base_ses_v_obs ~ safetydsh, data=oe[oe$cohort=="PartialNx",])
t.test(changerank_base_v_base_ses ~ safetydsh, data=oe[oe$cohort=="PartialNx",])


t.test(changerank_base_v_obs ~ safetydsh, data=oe[oe$cohort=="RadNx",])
t.test(changerank_base_ses_v_obs ~ safetydsh, data=oe[oe$cohort=="RadNx",])
t.test(changerank_base_v_base_ses ~ safetydsh, data=oe[oe$cohort=="RadNx",])

    group_by(cohort, safetynaph) %>%
  summarise(
    mean(changerank_base_v_obs),
    mean(changerank_base_ses_v_obs),
    mean(changerank_base_v_base_ses)
  ) %>% t() %>% as.data.frame()


View(pred)
oe %>% 
  filter(cohort=="Cystectomy") %>% 
  ungroup() %>%
  select(oshpd_id, r_obs, r_base, r_base_ses, starts_with("changerank")) %>%
  arrange(desc(changerank_base_v_obs))


oe %>%
  group_by(cohort) %>%
  do(
    base_v_obs_est = t.test(changerank_base_v_obs ~ safetynaph, data=.)$estimate,
    base_v_obs_pval = t.test(changerank_base_v_obs ~ safetynaph, data=.)$p.value,
    base_ses_v_obs_est = t.test(changerank_base_ses_v_obs ~ safetynaph, data=.)$estimate,
    base_ses_v_obs_pval = t.test(changerank_base_ses_v_obs ~ safetynaph, data=.)$p.value,
    base_v_base_ses_est = t.test(changerank_base_v_base_ses ~ safetynaph, data=.)$estimate,
    base_v_base_ses_pval = unlist(t.test(changerank_base_v_base_ses ~ safetynaph, data=.)$p.value)
  ) %>% t() %>% as.data.frame()


# change in rank in base model compared to observed


# change in rank in base model with SES compared to observed
# t.test(changerank_base_ses_v_obs ~  safetynaph, data=ranks)
# wilcox.test(ranks$p_base_ses, ranks$p_base, paired = T)
# 
# # change in rank in base model with SES compared to observed
# t.test(changerank_base_v_base_ses ~  safetynaph, data=ranks)
# wilcox.test(ranks$p_base_ses, ranks$p_base, paired = T)


```

```{r rankingfigs, eval=F}
# 30d Readmissions for cystectomy by safety net status
pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh)) %>%
ggplot(aes(x=reorder(oshpd_id, -p_obs), y=100*p_obs+.5, fill=safetydsh)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Observed 30 Day Readmission Rate for Cystectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))


pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh)) %>%
ggplot(aes(x=reorder(oshpd_id, -p_base), y=100*p_base+.5, fill=safetydsh)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Predicted 30 Day Readmission Rate for Cystectomy by Safety Net Status (base)", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

pred %>% filter(cohort=="Cystectomy" & !is.na(safetydsh)) %>%
ggplot(aes(x=reorder(oshpd_id, -p_base_ses), y=100*p_base_ses+.5, fill=safetydsh)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="Predicted 30 Day Readmission Rate for Cystectomy by Safety Net Status (base+SES)", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

# 30d Readmissions for Partial Nephrectomy by safety net status
pred %>% filter(cohort=="PartialNx" & !is.na(safetydsh)) %>%
ggplot(aes(x=reorder(oshpd_id, -p_obs), y=100*p_obs+.5, fill=safetydsh)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="30 Day Readmission Rate for Partial Nephrectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))

# 30d Readmissions for Radical Nephrectomy by safety net status
pred %>% filter(cohort=="RadNx" & !is.na(safetydsh)) %>%
ggplot(aes(x=reorder(oshpd_id, -p_obs), y=100*p_obs+.5, fill=safetydsh)) +
  geom_bar(stat="identity", width=0.7, position = position_dodge(width=0.2)) +
  labs(title="30 Day Readmission Rate for Radical Nephrectomy by Safety Net Status", x=NULL, y="30 Day Readmission Rate (%)") +
  scale_fill_brewer(palette = "Paired", name="Safety Net Status", labels=c("No", "Yes")) +
  theme_few() + 
  theme(axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  theme(plot.background = element_rect(fill=bg), legend.background= element_rect(fill=bg))
```

```{r eval=F}
ranks %>%
  filter(cohort=="Cystectomy") %>%
  filter(safetynaph==T) %>%
  select(oshpd_id, r_obs, r_base, r_base_ses) %>%
  arrange(desc(r_base_ses)) %>%
  write.csv("temp.csv")

 

wilcox.test(r_base_ses ~ safetynaph, data=ranks[ranks$cohort=="Cystectomy",])
t.test(r_base_ses ~ safetynaph, data=ranks[ranks$cohort=="Cystectomy",])$estimate[[1]]
t.test(r_base_ses ~ safetynaph, data=ranks[ranks$cohort=="Cystectomy",])$estimate[[2]]
```











